\chapter{Acknowledgements}
\vspace{-1cm}
This thesis would never have been possible without the ideas, friendship, support and assistance of numerous people.
Foremost among them is indubitably \thought{Dr Jared Cole}.
Whilst he may have balked my attempts to investigate the crazy world of AdS/CFT and holographic superconductivity when we first met, this was probably the only time he discouraged the hare-brained scheme \emph{de jour}.
Always approachable and engaging, it has been a continual joy to work with him -- even if photographic evidence suggests I distrust his opinions.

\thought{Professor Salvy Russo} has been a valued mentor since 2007.
If he's not winning karate championships one point away from disqualification, he's writing proofs by intimidation on the white board in front of undergraduates.
This take no-prisoners-attitude is reflected in his dedication and meticulousness towards both his research and his students -- even with the constant pressures the title of Deputy Dean bestows upon him.

A special thanks to all members past and present of the \thought{Chemical and Quantum Physics Group}.
I owe much to \thought{Dr Manolo Per} and \thought{Dr Akin Budi}, both of whom spent a great deal of time tutoring me in the art of numerical modelling during the late undergrad years.
\thought{Jan Jeske}, for putting up with my rants; contributing succinct and useful information each time I ran out of breath.
Also for being a wonderful `working' holiday companion and introducing me to a number of fantastic international colleagues.
\thought{David Ing} and \thought{Jesse Vaitkus} for actively participating in, if not instigating office shenanigans.
Only after offering valuable insight that greatly advances the scientific endeavour, of course.
\thought{Kelly}, \thought{Daniel}, \thought{Jackson}, \thought{Martin},  \thought{Muhammad}, \thought{Chris}, \thought{George} and the non-CQP members of the Engine Room for a great working environment, as well as the constructive and encouraging input over the years.
\thought{Martin}: I hope you uncover more about this elusive defect during your candidature than is printed on these pages.

My supervisors at DSTO: %
\nomdef{ADSTO}{DSTO}{Defence Science and Technology Organisation}%
\thought{Dr Milan Jamriska} and \thought{Dr Alex Skvortsov} for their patience, understanding and encouragement.
Furthermore, their acceptance that I may be off doing something other than my work there -- without warning, at the drop of a hat.

Finally, my family for their continual encouragement and for at least attempting to not zone out when I discuss the elegance of \sw{Haskell} or the why the collective odium towards the \sw{jet colormap} is completely warranted. 